Msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-15 paper.tex
make refs appear

\title{msprime 1.0: an efficient and extensible coalescent simulation framework}
\author{Author list to be filled in
}
% \address{

@@

% other simulators
Hudson's \ms\ optionally includes gene conversion and so does
MaCS~\citep{chen2009fast}, while scrm~\citep{staab2014scrm} does not
support gene conversions.
As bacterial recombination can be modeled analogously to eukaryotic allelic
gene conversion, simulators for microbial evolution often include gene conversion
instead of recombination.
This includes the backward simulator SimBac~\citep{brown2016simbac},
the SMC based approach used in FastSimBac~\citep{DeMaio2017},
and forward in time tools within the SLiM framework~\citep{Cury2020}.

>>>>

\title{Msprime 1.0: an efficient and extensible coalescent simulation framework}
\author{Author list to be filled in
}
% \address{

@@

% other simulators
Hudson's \ms\ optionally includes gene conversion and so does
MaCS~\citep{chen2009fast}, while scrm~\citep{staab2015scrm} does not
support gene conversions.
As bacterial recombination can be modeled analogously to eukaryotic allelic
gene conversion, simulators for microbial evolution often include gene conversion
instead of recombination.
This includes the backward simulator SimBac~\citep{brown2016simbac},
the SMC based approach used in FastSimBac~\citep{DeMaio2017},
and forward in time tools within the SLiM framework~\citep{Cury2020}.
